Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 schemes.tex

Therefore, in \ac{TSNC}, a simple procedure for controlling this probability
is to gradually increase the coding density as the \ac{dof}\footnote{We refer
as degrees of freedom to the dimension of the linear span from the coded
packets that a decoder has at a given point} increases, e.g. as the
cardinality of the set of \ac{l.i.} coded packets increases. This enables
\ac{TSNC} to significantly reduce the complexity, particularly in the
beginning of the transmission process and also to control the decoding
delay. For \ac{TSNC}, we define the budget, $B \geq g$, to be a target
number of coded packets a transmitter wants to send to a receiver
for decoding a generation of $g$ packets.

The difference between $B$ and $g$ is equal to the losses in the channel and the
losses due to linear dependencies. Therefore, in a lossless channel, the budget
is
\begin{equation}\label{eq:budget}
    B(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)},
\end{equation}

where $P(i,n,d)$ is the probability of receiving an innovative coded packet
after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our implementations, we considered the the upper bound for the innovation probability from \cite{feizi2014tunable}, given as
\begin{equation}
    P(i,g,d)\geq 1-(1-d)^{n-i}
\end{equation}

Provided a desired budget $B$ and the \ac{dof} of the decoder, an encoder
can estimate the required coding density for the packets to not exceed the
budget. In our implementation, we use feedback packets to provide the
encoder an estimate of the decoder \ac{dof} at pre-defined points of the
transmission process. The points in the process occur when a decoder
obtains a given amount of \ac{dof}. In our implementation, we define $r(k),\
k \in [1, \ldots)$ as the rank $r$ of the decoder\footnote{The rank of
a decoder is the rank of its coding matrix at a given point in the
transmissions process.} where a decoder has to send the $k$-th feedback in
\eqref{eq:feedback_dofs}.
%
\begin{equation}\label{eq:feedback_dofs}
    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in [1,\ldots)
\end{equation}
%
At the beginning of the transmission process, we assume that the encoder
starts with an initial coding density that has been calculated depending to
the budget. According to \eqref{eq:feedback_dofs}, a decoder sends feedback
once it has obtained (rounded down) $g/2,\ 3g/4,\ 7g/8,\ \ldots$  degrees of
freedom. The total amount of feedback for this scheme will depend on the
generation size. Still, we have an implementation that limits the amount of
feedback to be sent from the decoder in [\textbf{reference}].\todot{@Chres this reference is missing}

The transmissions made between feedback packets are called the density regions
since the same estimated density is used for encoding sparse packets. Once new
feedback is received, an encoder recalculates the coding density for the new
region until the next feedback packet is received. Before the coding density can
be estimated, it is essential that the encoder has a good estimate of the
decoder \ac{dof}, but also the remainder of the total budget. To calculate the
density, we use bisection to estimate a fixed density for the density region
that satisfies the budget for the $k$-th density region:
\begin{equation}
B(s(k-1),r(k),g,d) = \sum^{r(k)}_{i=r(k-1)} \frac{1}{P(i,g,d)} = \sum^{r(k)}_{i=r(k-1)} \frac{1}{1-(1-d)^{g-i}} = \frac{B}{2^k}, k\in [1,...).
\end{equation}
%
% Where the budget is half of the remaining budget for all the density regions
% except the last one, to which it is assigned the remaining of the budget.
The feedback scheme based on the rank reports of \eqref{eq:feedback_dofs}
roughly splits the remaining coding regions in two halves. In other
words, the first half is the region where the encoder currently operates. Once
an encoder finishes with this region, it proceeds with second half where again
it splits this into to two region and so on until it finishes on transmitting
the whole generation. This is also the case for the budget that is split equally
among the two new regions. The very last region will be assigned the full
remainder of the total budget and the coding density will not vary.

>>>>

Therefore, in \ac{TSNC}, a simple procedure for controlling this probability
is to gradually increase the coding density as the \ac{dof}\footnote{We refer
as degrees of freedom to the dimension of the linear span from the coded
packets that a decoder has at a given point} increases, e.g. as the
cardinality of the set of \ac{l.i.} coded packets increases. This enables
\ac{TSNC} to significantly reduce the complexity, particularly in the
beginning of the transmission process and also to control the decoding
delay. For \ac{TSNC}, we define the budget, $b \geq g$, to be a target
number of coded packets a transmitter wants to send to a receiver
for decoding a generation of $g$ packets. In some scenarios, we may set
$e$ defined as the excess of \ac{l.d.} packets sent from the encoder.
This helps to also define the budget as $b = g + e$.

The difference between $b$ and $g$ is equal to the losses in the channel and the
losses due to linear dependencies. Therefore, in a lossless channel, the budget
is
\begin{equation}\label{eq:budget}
    b(g,d)=\sum^{g-1}_{i=0}\frac{1}{P(i,g,d)}
\end{equation}

where $P(i,g,d)$ is the probability of receiving an innovative coded packet
after receiving $i$ \ac{l.i.} packets with a coding density $d$. In our implementations, we considered the the upper bound for the innovation probability from \cite{feizi2014tunable}, given as
\begin{equation}
    P(i,g,d)\geq 1-(1-d)^{g-i}
\end{equation}

Provided a desired budget $b$ and the \ac{dof} of the decoder, an encoder
can estimate the required coding density for the packets to not exceed the
budget. In our implementation, we use feedback packets to provide the
encoder an estimate of the decoder \ac{dof} at pre-defined points of the
transmission process. The points in the process occur when a decoder
obtains a given amount of \ac{dof}. In our implementation, we define $r(k),\
k \in [1, \ldots)$ as the rank $r$ of the decoder\footnote{The rank of
a decoder is the rank of its coding matrix at a given point in the
transmissions process.} where a decoder has to send the $k$-th feedback in
\eqref{eq:feedback_dofs}.
%
\begin{equation}\label{eq:feedback_dofs}
    r(k) = \floor{g\cdot \left[\frac{2^k -1}{2^k}\right]},\ k \in [1,\ldots)
\end{equation}
%
At the beginning of the transmission process, we assume that the encoder
starts with an initial coding density that has been calculated depending to
the budget. According to \eqref{eq:feedback_dofs}, a decoder sends feedback
once it has obtained (rounded down) $g/2,\ 3g/4,\ 7g/8,\ \ldots$  degrees of
freedom. The total amount of feedback for this scheme will depend on the
generation size. Still, we have an implementation that limits the amount of
feedback to be sent from the decoder in [\textbf{reference}].\todot{@Chres this reference is missing}

The transmissions made between feedback packets are called the density regions
since the same estimated density is used for encoding sparse packets. Once new
feedback is received, an encoder recalculates the coding density for the new
region until the next feedback packet is received. before the coding density can
be estimated, it is essential that the encoder has a good estimate of the
decoder \ac{dof}, but also the remainder of the total budget. To calculate the
density, we use bisection to estimate a fixed density for the density region
that satisfies the budget for the $k$-th density region:
\begin{equation}
b(s(k-1),r(k),g,d) = \sum^{r(k)}_{i=r(k-1)} \frac{1}{P(i,g,d)} = \sum^{r(k)}_{i=r(k-1)} \frac{1}{1-(1-d)^{g-i}} = \frac{b}{2^k}, k\in [1,...).
\end{equation}
%
% Where the budget is half of the remaining budget for all the density regions
% except the last one, to which it is assigned the remaining of the budget.
The feedback scheme based on the rank reports of \eqref{eq:feedback_dofs}
roughly splits the remaining coding regions in two halves. In other
words, the first half is the region where the encoder currently operates. Once
an encoder finishes with this region, it proceeds with second half where again
it splits this into to two region and so on until it finishes on transmitting
the whole generation. This is also the case for the budget that is split equally
among the two new regions. The very last region will be assigned the full
remainder of the total budget and the coding density will not vary.
